Current Affairs: Utilizing Oxford Nanopore Sequencing Data to Detect Non-Canonical DNA Structures

### 2024-01-26 jan30meeting_pres1/may30ccgmeeting.tex
updates

	%%%%% APPRACH SECTION BEGINS HERE, 2 SLIDES
	\section{Approaches}

	\begin{frame}{A Promising New Approach}
		\textbf{\color{blue}Tissue cSL Load:} Median cSL load value across all samples of each tissue type

		\centering
		\includegraphics[width=8cm, height=6cm]{tcl1.png}
		\footnotetext[5]{\tiny\cite{cheng2021synthetic}}
	\end{frame}

@@

	\begin{frame}{Where did the Data come From?}
		A recently published reference set of genome-wide cSLs common to many cancer types was utilized
		\begin{center}
				\includegraphics[width=6cm,height=6cm]{corenet.png}
		\end{center}
	\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}

>>>>

	%%%%% APPRACH SECTION BEGINS HERE, 2 SLIDES

	\begin{frame}{Third Generation Sequencing: A Promising New Approach}
		\textbf{\color{blue}Single Molecule, Real Time Sequencing (SMRT):} Pacbio's third generation sequencing machine
		\begin{itemize}
			\item Emits a fluorescent pulse when nucleotide is detected - the time interval between two pulses is called the interpulse duration (IPD)
			\item Guiblet et al (2018), showed that there is a significant divergence between IPDs in non-B DNA motif regions compared to B-DNA regions
		\end{itemize}

		\centering
		\includegraphics[width=10cm, height=4.5cm]{sequencing_evolution.png}
	\end{frame}

@@

	\begin{frame}{Predicting Non-B Structures From Nanopore Sequencing}
		A recently published reference set of genome-wide cSLs common to many cancer types was utilized
		\begin{center}
				\includegraphics[width=6cm,height=6cm]{corenet.png}
		\end{center}
	\footnotetext[2]{\tiny\cite{lee2018harnessing}}
	\end{frame}
